Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-11 Paper/Manuscript_Stats&Comp/reply_letter_STCO.tex

In the Leukemia data set case study, we present a 4D HSGP model. We have applied the diagnostic tool and have been able to easily discover the optimal values for $c$ and $m$ that allows for a significantly faster performance than using the exact GP. Without the guidance of the diagnostic tool, a user would have to go through several more trials until finding a sufficiently accurate solution, which would result in substantially increased human and computer time requirements.

@@

The main comparison that we focus on is the Hilbert space basis function approximation (our HSGP method) against the exact GP model. In all comparisons, the inference conditional on the model is assumed to be accurate. In other words, we compare the exact to an approximate model, using asymptotically correct inference. For this purpose, we have used efficient dynamic HMC, the MCMC convergence diagnostics did not reveal problems, and thus the accuracy of the inference itself can be considered good.

While we agree that other comparisons could interesting as well, for example MCMC vs. variational inference, they would blow up the already extensive scope of the paper. Some comparisons of MCMC and variational inference for basis function GPs can be found in

@@

Further comparisons of the Hilbert space basis function approximations against other GP approximations are provided by Solin and Särkkä (2020), which is cited prominently in our paper.

>>>>

In the Leukemia data set case study, we present a 4D HSGP model. We have applied the diagnostic tool and have been able to easily discover the optimal values for $c$ and $m$ that allows for a significantly faster performance than using the exact GP. Without the guidance of the diagnostic tool, a user would have to go through several trials until finding a sufficiently accurate solution, which would result in substantially increased human and computer time requirements.

We have also added a new case study to Section 5 which consists of wiggly 2D and 3D simulated data sets, where have applied the diagnostic procedure too. Even though the diagnostic was designed for unidimensional kernels, we demonstrate its applicability and usefulness in multidimensional cases by diagnosing the different dimensions in each iteration individually. 
%It allows us to find the optimal solution with the minimum requirements that can be essential to use the HSGP model in multidimensional cases.
In this new case study, we have also included a brief discussion and presentation of additional results concerning computational cost in 2D, 3D, and 4D.

@@

In the paper, we focus on the comparison between the Hilbert space basis function approximation (HSGP method) against an exact GP inference. 
%In all comparisons, the inference conditional on the model is assumed to be accurate. In other words, we compare the exact to an approximate model, using asymptotically correct inference.
For this purpose, we have used the efficient dynamic HMC algorithm with careful monitoring of the relevant MCMC convergence diagnostics to ensure that the Markov chains have mixed properly, and thus the accuracy of the inference itself can be considered good.

While we agree that other comparisons could interesting as well, for example MCMC vs. variational inference, they would blow up the already extensive scope of the paper. However, we want to emphasize that several comparisons of MCMC and variational inference for basis function GPs can be found in

@@

Furthermore, Solin and Särkkä (2020) compare the HSGP approximation to a range of difficult low-rank Gaussian process approximation methods based on inducing points. The results show that the HSGP approximation yields superior accuracy and therefore, our study is focused on the comparison against the exact model.

 %of the Hilbert space basis function approximations against other GP approximations are provided by ,
